Think deep for reef resilience

### 2025-08-10 paper/paper_draft.qmd
Add quantification of cluster assignment consistency

Comparing across GCMs, it is common for reefs to switch cluster level, including from low to
high and high to low cluster transitions (@sfig-gcm-bioregion-cluster-assignment). This is
expected as spatial differences in GCM DHW timeseries result in reefs being impacted at
different relative magnitudes within their management area across GCMs.

@@

>>>>

Comparing across GCMs, it is common for reefs to switch cluster level, including from low to
high and high to low cluster transitions (@sfig-gcm-bioregion-cluster-assignment). Of 2429
reefs, 20% (503) of reefs have consistent management area scale cluster assignment across
all GCMs. This high assignment variability across GCMs is expected as spatial differences in
GCM DHW timeseries result in reefs being impacted at different relative magnitudes within
their management area across GCMs.

@@

\[**BG: Need to ensure that methods explain why I use CID here to quantify differences
between low and high cluster median timeseries.**\]
